---
title: "Chapel Hill-Carrboro COVID Community Support Resources"
output:
    flexdashboard::flex_dashboard:
        orientation: rows
        social: menu
runtime: shiny
---

<!-- This code section is for initial package loading and global setup options -->

    ```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(leaflet)
library(googlesheets4)
library(reactable)
    
sheets_deauth() # Make googlesheets4 skip authentification, since we're using a public sheet
```

<!-- This code section is for retrieving data from the Google Sheet -->

```{r get-data, message=FALSE, include=FALSE} 
# Create a function that reads the data from Google.
# For now, a roundabout approach. Streamline in future.
# See detail here: https://www.andrewheiss.com/blog/2020/01/01/flexdashboard-dynamic-data/
load_remote_data <- function() {
    read_sheet(ss = "1NNo23idWdFofp5LbBS_3S6EQfzgbe1sVgr2GRAjucA0", 
               sheet = "resources",
               col_types = "??????cnn???????TTnnnnnnnn")
}
remote_data <- load_remote_data() %>%
  mutate(index = row_number())
```

<!-- This code section is for data processing -->

```{r data-processing, message=FALSE, include=FALSE}
# data object for Leaflet map
map_data <- reactive({
  remote_data %>%
    filter(is.na(lat) != TRUE & is.na(lon) != TRUE) %>%
    filter(resource == input$resource) %>%
    pivot_longer(cols = 19:25, names_to = "days", values_to = "des") %>%
    filter(is.na(des) != TRUE & des != 0) %>%
    filter(days %in% input$day) %>%
    pivot_wider(names_from = "days", values_from = "des")
})

# create a new object that grabs the columns from remote_data that should be included in the table 
include_in_table <- reactive({
  map_data() %>%
    select(provider, address, city, state, zip, details_1, details_2)
})

# create a new data object for only the row selected on the map
selected_marker <- reactive({
  map_data() %>%
    filter(index == input$map_marker_click$id) %>%
    select(provider, address, city, state, zip, details_1, details_2)
})

```

<!-- This code section is for rendering static UI outpus -->

```{r static-rendering, message=FALSE, include=FALSE}
# Sum all active free meal resources 
output$meal_count <- renderValueBox({
  num_free_meals <- count(filter(remote_data, resource == "meal" & free == 1 & status == "active"))
  valueBox(
    value = num_free_meals,
    icon = "fa-utensils", # icon from https://fontawesome.com/icons/utensils?style=solid
    color = "primary" # https://rstudio.github.io/shinydashboard/appearance.html#statuses-and-colors
  )
})

# Sum all active meal resources with curbside pick-up
output$restaurant_count <- renderValueBox({
    num_curbside <- count(filter(remote_data, resource == "meal" & free == 0 & status == "active" & access_type == "drive-up"))
    valueBox(
        value = num_curbside,
        icon = "fa-car", #icon from https://fontawesome.com/icons/car?style=solid
        color = "success" #https://rstudio.github.io/shinydashboard/appearance.html#statuses-and-colors
    )
})

# Sum all active resources with senior shopping hours
output$senior_count <- renderValueBox({
    num_senior <- count(filter(remote_data, status == "active" & access_type == "senior shopping hours"))
    valueBox(
        value = num_senior,
        icon = "fa-history", #icon from https://fontawesome.com/icons/history?style=solid
        color = "primary" #https://rstudio.github.io/shinydashboard/appearance.html#statuses-and-colors
    )
})

# Sum all active resources with discounts for medical workers
output$discount_count <- renderValueBox({
    num_discount <- count(filter(remote_data, status == "active" & access_type == "medical worker discount"))
    valueBox(
        value = num_discount,
        icon = "fa-user-md", #icon from https://fontawesome.com/icons/user-md?style=solid
        color = "success" #https://rstudio.github.io/shinydashboard/appearance.html#statuses-and-colors
    )
})

```

<!-- This code section is for rendering reactive UI outpus -->

```{r reactive-rendering, message=FALSE, include=FALSE}
# Creating main Leaflet map using reactive map data
output$map <- renderLeaflet({
  
  map_data() %>%
  leaflet(width = "80%") %>%
    addTiles(
      urlTemplate = "https://api.maptiler.com/maps/streets/{z}/{x}/{y}@2x.png?key=TxvhrAmR6qR1BMLNZjOj",
      attribution = htmltools::HTML("<a href='https://www.maptiler.com/copyright/' target='_blank'>© MapTiler</a> <a href='https://www.openstreetmap.org/copyright' target='_blank'>© OpenStreetMap contributors</a>"),
      group = "Detailed Streets"
    ) %>%
    addTiles(
      urlTemplate = "https://api.maptiler.com/maps/positron/256/{z}/{x}/{y}@2x.png?key=TxvhrAmR6qR1BMLNZjOj",
      attribution = htmltools::HTML("<a href='https://www.maptiler.com/copyright/' target='_blank'>© MapTiler</a> <a href='https://www.openstreetmap.org/copyright' target='_blank'>© OpenStreetMap contributors</a>"),
      group = "Positron"
    ) %>%
    addMarkers(
      layerId = ~index,
      lng = ~lon, lat = ~lat,
      popup = paste(
        "<b><a href='", map_data()$web_link, "'>", map_data()$provider, "</a></b><br/>",
        "<b>Address:</b>", map_data()$address, ",", map_data()$city, ",", map_data()$state, ",",
        map_data()$zip, "<br/>", "<b>Phone:</b> ", map_data()$contact, "<br/><b>Notes:</b> ", map_data()$details_1, "<br/>", map_data()$details_2
      ),
      clusterOptions = markerClusterOptions(spiderfyOnMaxZoom = TRUE)
    ) %>%
    addLayersControl(baseGroups = c(
      "Detailed Streets",
      "Positron"
    ))
})

# Generating main table using reactive table data
output$table <- renderReactable({
  reactable(include_in_table(),rownames = FALSE, resizable = TRUE,
            defaultPageSize = 5,striped = TRUE,
            columns = list(
              provider = colDef(name = "Provider"),
              address = colDef(name = "Address"),
              city = colDef(name = "City"),
              state = colDef(name = "State"),
              zip = colDef(name = "Zip"),
              details_1 = colDef(name = "Notes"),
              details_2 = colDef(name = "Addtl. Notes")
            ))
})

# Generate table to display information for the selected feature
output$selected_table <- renderReactable({
  req(input$map_marker_click)
  
  reactable(selected_marker(), rownames = FALSE, resizable = TRUE,
            defaultPageSize = 1,
            columns = list(
              provider = colDef(name = "Provider"),
              address = colDef(name = "Address"),
              city = colDef(name = "City"),
              state = colDef(name = "State"),
              zip = colDef(name = "Zip"),
              details_1 = colDef(name = "Notes"),
              details_2 = colDef(name = "Addtl. Notes")
            ))
})

```

```{r event-handling, include=FALSE, message=FALSE}
# Click event for the map (will use to generate chart)
click_marker <- eventReactive(input$map_marker_click, {
    x <- input$map_marker_click
    return(x)
  })

output$text <- renderPrint({ input$map_marker_click$id })
```


<!-- This section should be utilized for inline HTML and CSS -->

<link href="https://fonts.googleapis.com/css?family=Roboto&display=swap" rel="stylesheet">
<style>
* {font-size: 100%; font-family: Roboto, sans-serif;}
.navbar-brand {
    float:none;
    font-size: 19px;
    line-height: 21px;
    height: 50px;
    display: block;
}

@media screen and (max-width: 576px) {
.navbar-brand {
    padding: 5px 15px;
    font-size: 17px;
}

}
</style>

<!-- End of inline HTML and CSS section -->

<!-- The section defines the global sidebar for the dashboard -->

Sidebar {.sidebar}
======================================================================
    
```{r}
# selectInput(inputId = "language",label =  "Choose your language",
#             selected = "English", selectize = TRUE,
#   choices = c("English", "Español", "Française", "中文／Chinese", "日本語/ Japanese", "عربي/ Arabic", "한국어/ Korean", "Karen")
# )
    
selectInput(inputId = "resource",label =  "What do you need?",
            selectize = TRUE, selected = "meal",
            choices = c(
              "Meals" = "meal", "Groceries" = "grocery",
              "Pharmacy" = "pharmacy", "Childcare for medical workers" = "childcare"
              )
            )

selectInput(
  inputId = "day", label = "What days do you need this resource?",
  selectize = TRUE, multiple = TRUE, selected = "mon",
  choices = c(
    "Monday" = "mon", "Tuesday" = "tues", "Wednesday" = "wed",
    "Thursday" = "thr", "Friday" = "fri",
    "Saturday" = "sat", "Sunday" = "sun"
  )
)

checkboxGroupInput(inputId = "cost",label =  "Resource type",
  choices = c("Free resources" = "free", "Paid resources" = "paid")
)

checkboxGroupInput(inputId = "access",label =  "Access",
  choices = c("Pick-up", "Drive-up", "Delivery")
)

checkboxGroupInput(inputId = "time",label =  "Times available",
  choices = c("Morning", "Afternoon", "Evening", "24 hour")
)

# radioButtons("bus", "Show bus routes?", #Bus routes might be too much for now
# choices = c("on", "off"))

hr()

helpText(sprintf("Last updated: %s", format(Sys.time(), "%b %d, %Y at %I:%M %p")))

verbatimTextOutput("text")
```

<!-- This section defines the elements for the main landing page -->

Resources
======================================================================

Row
----------------------------------------------------------------------
    
### Free meal locations {.value-box}
    
```{r}
valueBoxOutput("meal_count")
```


### Restaurants with curbside pick-up {.value-box}

```{r}
valueBoxOutput("restaurant_count")
```

### Senior shopping hours {.value-box}

```{r}
valueBoxOutput("senior_count")
```


### Discounts for medical workers {.value-box}

```{r}
valueBoxOutput("discount_count")
```

Row {.tabset .tabset-fade}
-------------------------------------

### Map View

```{r}
leafletOutput("map")
``` 

### Full Table View

```{r}
reactableOutput("table")
```

Row {data-height=200}
----------------------------------------------------------------------

### Selected Resource

```{r}
reactableOutput("selected_table")
```

<!-- This section defines elements for an additional About page -->

About
======================================================================

### About the project

#### This project IS….
- A website/webapp with an interactive community map.
- A tool to help our communities and neighbors locate resources.
- A collaborative effort connected to local officials and support organizations.
- An open project that can be quickly adapted to other locations & future needs.
- Resources we might want to map:
- Where can I find a free meal?
- Where can I find free diapers/tp/personal care items?
- Where can I find a drive-up pharmacy?
- Where can I find a market with age-60+ shopping hours?

#### This project is NOT…..
- A map of COVID-19 cases.
- Information related to emergency medical resources.
- Outdated information or a dilution of other information channels.

### How can you help?
Insert information and links for how people can help
